Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-10-17 2016-Weak-FH-Bisim/WeakBisim.tex

@@

Fig. \ref{SimpleProt:Spec} shows the Schema of this system, and on the right side, its global specification, expressed as a pNet: it should be equivalent to a simple system where the holes would be connected by a perfect reliable medium.

The full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium.

\section{A model of process composition}\label{sec:OT}
\TODO{Commenter la figure 2}

@@

\end{document}
\section{Examples of Lotos laws}
Possible Lotos small examples:

>>>>

\begin{figure}[t]
   \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
   \includegraphics[width=6.5cm]{XFIG/SimpleProt2-Spec}
   \caption{Specification pNet Schema and Specification}
   \label{SimpleProt:Spec}

@@

Fig. \ref{SimpleProt:Spec} shows the Schema of this system, and on the right side, its global specification, expressed as a pNet. 
The full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium. Fig. \ref{SimpleProt:Spec}, right, shows the pNet representing this global specification.

Fig. \ref{SimpleProt:Impl} show the pNet model of the protocol. When the medium detects an error (modeled by a local $\tau$ action), it sends back a $m\_error$ message to the $Sender$. The $Sender$ increments its error counter $c$, and resend the message (including $c$) to the medium, that will, eventually, transmit $m,c$ to the receiver.

\section{A model of process composition}\label{sec:OT}

@@

\section{Full details of the Simple Protocol Example}

Let us start with the basic version, with no error counter.

\section{Examples of Lotos laws}
Possible Lotos small examples:
